### 2022-10-25 manuscript.Rmd
Use word count from MS Word
Fix label in Supplementary TFR plot

  Number of words: 212 (abstract), 644 (introduction), 1,487 (discussion)

@@

```{r, figs2, cache=!run$figures, fig.height=11, fig.cap="(ref:figs2-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(
    tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed"
  ),
  p_cluster = p_cluster,
  condition_plus = "Informed",
  condition_minus = "Exclude_informed"
)
```

>>>>

  Number of words: 215 (abstract), 632 (introduction), 1,443 (discussion)

@@

```{r, figs2, cache=!run$figures, fig.height=11, fig.cap="(ref:figs2-caption)"}
# Create topographic plots for control analysis of event-related power
plot_tfr_topos(
  filter(tfr_grand_ave, phase == "Insight"),
  filter(
    tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed"
  ),
  p_cluster = p_cluster,
  condition_plus = "Informed",
  condition_minus = "Exclude_informed",
  title_conditions = "Informed - failed"
)
```
